%\subsection{Proposed Models}
Our approach biases the statistics of the conditional deviatoric pressure Hessian using the history of the VGT (as in the RDGF, RFD, and Tetrad models), while avoiding postulating the exact functional form; instead allowing it to be data-driven using PIML (as in TBNN model).

We do this by augmenting the inputs to the feed-forward portion of the TBNN, the idea being to bias the statistics of the invariants, while believing that the tensors derived from the local-in-time VGT are sufficient to span the function space.

    % \item \textbf{RDGF with TBNN output as upstream condition}
    
    % The most logical next step in this progression of deformation models is to enrich the RDGF model using the output of the TBNN. That is, eq(\ref{eq:rdgf_upstream}) becomes
    % \begin{equation} \label{eq:tbnn_rdgf_upstream}
    %     \langle \tilde{P}_{ij} | A \rangle \approx \frac{1}{3} \langle \tilde{P}_{kk} | A \rangle \delta_{ij} + \sum_{n=1}^{10} g_\theta^{(n)}(\lambda_1, \dots, \lambda_5)T^{(n)}
    % \end{equation}
    
    % We believe this has the potential to enrich both models, as Tian et.al, found the different values of parameters in eq(\ref{eq:rdgf_coefs}), and importantly has access to distributions of those parameters. Further, the un-truncated tensor basis has the ability to better represent strongly intermittent conditions. On the other hand, the RDGF model ties this prediction to the local fluid deformation, incorporating temporal information to the local-in-time TBNN.
\subsection{Temporal Convolution}
Motivated by the deformation tensor in eq(\ref{eq:defTensor})
\begin{equation}
  D(t) = \text{Texp}\left(\int\limits_0^t dt' A(t')\right) = \lim_{N\to \infty} \prod_{i = 0}^N \left( e^{A(t_i)\Delta t} \right),
\end{equation}
Each term on the right-hand side of eq(\ref{eq:defTensor}) can be expanded to
\begin{equation}
  e^{A_m \Delta t} = I + \sum_{i=0}^N \frac{1}{i!} \left( \Delta t A_m \right)^i = I + \Delta t A_m+ \bigO(\Delta t^2)
\end{equation}
So that, taking the leading order in $\Delta t$, we obtain the first-order approximation of the deformation tensor
\begin{equation}
  D = I + \Delta t \sum_{n=N}^0 A_n + \bigO(\Delta t^2)
\end{equation}

Therefore, the simplest of our proposed models augments the set of invariants using a learned temporal convolution
\begin{equation} \label{eq:tc_pred}
  \hat{H} = \sum_{n=1}^{10} g_\theta^{(n)}(\lambda_1, \dots, \lambda_5, C)T^{(n)}
\end{equation}
with
\begin{equation}
    C(t) = \sum_{t_f}^{t_f-\Delta t \cdot n} \zeta_n A_n
\end{equation}
where the scalar $\zeta_n$ are learned simultaneously with the parameterization of the scalar $g$ functions.

This model avoids prejudicing the prediction with a specific phenomenological theory of history importance, at the cost of increased computational overhead (namely storing history for each VGT). However, because of the simple structure, the learned $\zeta$'s may inform a temporal correlation in the VGT that is useful in the prediction of the deviatoric pressure Hessian. An extreme case of very short time correlations would reinforce the hypothesis presented in RDGF, while longer temporal correlations would support longer memory approaches e.g., \cite{tian2021_MZ}.

\subsection{Time-Ordered Exponential}
Further, we may hypothesize the exact form of history, replacing $C$ in Eq.~(\ref{eq:tc_pred}) by the true time-ordered exponential 
\begin{equation}
    W(t) = \text{Texp}\left(\int\limits_0^t dt' A(t')\right)
\end{equation}

\subsection{Ground Truth Data \& Training}
Our data is DNS of forced isotropic turbulence with $Re \approx 240$. Eularian data is generated, random points are sampled, VGT and pressure Hessian are constructed at these points using interpolation, and Lagrangian trajectories of these quantities are advanced using the Eularian velocity fields. We have 122k samples, each advanced for 1000 timesteps with $\Delta t = 3e\text{-}4$, representing approximately an inertial eddy turnover time. For each sample and each timestep, we have measured VGT, PH, and viscous terms. We use single timesteps, aggregated over Lagrangian paths separated in time by half an eddy turnover time, as labeled data. As observed by Parashar et.al \cite{parashar2020modeling}, the behavior and training of the TBNN is sensitive to choice of normalization. We follow Tian et.al choosing the physically inspired normalization by Kolmogorov timescale to normalize our input data (and thus the tensor basis itself)
\begin{equation}
  \tau = \frac{1}{\langle \norm{S_{ij}}_2^2 \rangle}
\end{equation}
However, recent work suggests this may be an additional hyperparameter to consider\cite{hyett2022applicability}.

We use a network architecture following Tian et.al's suggestion in their TBNN work\cite{tian2021}, refined using a hyperparameter search\cite{chollet2015keras} across network sizes and shapes, learning rates, and minibatch sizes for each augmentation to the TBNN. The network is trained to minimize the $L_2$ error between the ground truth and predicted pressure Hessian. That is, the optimal parameters are the solution to the optimization
\begin{equation}
  \min_\theta \norm{H - \hat{H}}_2^2
\end{equation}

% \subsubsection{Cramer Functions of Strain Rate Eigenvalues}
% Coarsely stated, the Cramer function (also more generally called the rate function) determines how quickly large deviations from a mean diminish. If we believe in the ability to close the equations for the deviatoric pressure Hessian locally, it is apparent that there must exist a relation between temporal correlations of the strain-rate tensor, and temporal correlations of the deviatoric pressure Hessian.

% \subsubsection{Gaussian Upstream Condition}
% The Gaussian upstream condition present in RDGF is convenient, but for short deformation time is known to be inaccurate. Via analysis of Lagrangian data, we can evaluate how long the deformation time must be to transform the Gaussian upstream condition to a distribution representative of fully developed turbulence. In particular, we can evaluate
% \begin{equation}
%     \min_{\Delta t} \ \norm{P^{(d)}_{gt} - P'^{(d)}_{\text{Gaussian}}(\Delta t)}
% \end{equation}
% where $P'^{(d)}_{\text{Gaussian}}(\Delta t)$ is the true deformation of the Gaussian upstream condition, by the ground truth VGT over a time $\Delta t$.

